### 2018-09-08 sections/signal_background_modeling.tex
Implemented remaining replies to CDS comments from Susumu Oda

The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR. The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates are subtracted. In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$. In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production. However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR. Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR. 
In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR will be allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.

>>>>

The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR. The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from 
$W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted. In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$. In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production. However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR. Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR. 
In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR will be allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
